\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex	
\usepackage{amssymb}
\usepackage{color}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{amsmath}

%SetFonts

%SetFonts


\title{QSS-2022-0063: Response to First Review}
\author{George Chacko}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
\section*{}

We thank the Editor for the opportunity to respond to a second round of critique. We thank both Reviewers for their professional courtesy of evaluating our manuscript again. Reviewer 2 offers no comment and appears satisfied. Reviewer 1 raises several points, which we appreciate. In our second revision, which accompanies this response, we have tried to offer greater clarity in terms of objectives and interpretation.

 \vspace{2 mm} 
 \emph{I thank the authors for considering my previous comments and for the extensive answers and clarifications. I have some comments, mostly regarding the empirical part of the paper.} 
 
 \vspace{2 mm} 
The authors appreciate  the reviewer's previous comments, which were helpful, thoughtful and constructively critical. Since the discussion in this cycle of critique and response seems to have broadened in scope, we recapitulate from the original submission and two rounds of critique and response in the next paragraph.

 \vspace{2 mm} In this manuscript, we seek to address the general, and often overlooked, limitation of disjoint clustering by presenting AOC, a method that post-processes an input clustering. The AOC method is principled and deterministic in its assignment of nodes to multiple clusters. We use Iterative K-core Clustering (IKC) as our test case for input clustering. The IKC method, based on the well-known k-core concept, has already been published (Wedell et al. 2022. https://doi.org/10.1162/qss\_a\_00184). In describing IKC in this manuscript for context, we have made every effort to avoid reproducing what is already in print. The use of marker nodes is to identify the subset of clusters of interest in this case and not to evaluate cluster quality. The balance of effort in this manuscript is tilted towards methods development over discovery.
 
 \vspace{2 mm}  
 \emph{The assignment of publications to the previously obtained clusters inevitably imply a trade-off between coverage and accuracy (similar to the trade-off between recall and precision in an information retrieval setting). Assigning more publications to a cluster and in addition assigning one publication to multiple clusters will lead to larger coverage of the clusters. In the paper, this is shown by the larger concentration of marker nodes in clusters after the AOC procedure. However, the larger coverage will likely also lead to irrelevant publications being assigned to clusters, making the clusters more hetrogenous. The empirical part of this paper does not address this trade-off. It can be noted that any methodology expanding cluster sizes by assigning publications to multiple clusters will likely lead to a higher cluster coverage of baseline publications, such as the marker nodes. The authors show the benefits of expanding the clusters in terms of marker node coverage in some clusters. However, the effect on the accuracy of clusters is not addressed. In my view, the trade-off between coverage and accuracy should be addressed to make it possible for the reader to judge whether AOC is successful or not.}

\vspace{2 mm} The analogy to precision and recall is not very obvious to us. However, the reviewer's concern seems to be that the multiple cluster assignments in AOC are somewhat indiscriminate. If so, we disagree. The criteria for assignment are the same as the criteria for clustering by IKC except that the limitation of disjoint clustering and effect of order in IKC is overcome\footnote{ We hope the following information will be helpful in clarifying the intent of AOC.  Specifically, the input to the IKC algorithm is a network $N$ and a parameter $k$. The output of the IKC algorithm is a collection of clusters, each of which has three specific properties: (i) the cluster is connected, (ii) every node in the cluster is adjacent to at least $k$ other nodes in the cluster, and (iii) each cluster has positive modularity. These properties of the IKC clusters are essentially the definition of what this algorithm considers  a minimum standard for being a ``valid" community.  We wish to point out that this is similar to text about the Constant Potts Model in Traag, Waltman, and Van Eyck (Scientific Reports, 2019) which indicates that ``communities should have a density of at least $\gamma$'', where $\gamma$ is the resolution parameter for the CPM criterion.  Similar text about modularity is found in Fortunato and Barth\'el\'emy (PNAS); they  say ``We conclude that, in a modularity-based framework, a subgraph $s$ with $l_s$ internal links and total degree $d_s$ is a 
module if $\frac{l_s}{L} - \left( \frac{d_s}{2L} \right) ^2 > 0$."  We put this more succinctly and say that any cluster with positive modularity should be considered valid. 
Later text in Fortunato and Barth\'el\'emy (PNAS) provides a stronger condition for being a ``module" by requiring that the modularity score be above 0.3, but the sense of the condition is still the same. Thus, for both modularity and CPM optimization, in essence there is a characterization of what is required for a cluster to be considered valid; the same is true for IKC, given the parameter $k$, any cluster with these three properties (connected, positive modularity, and every node is adjacent to at least $k$ other nodes) is valid. 

The set of clusters that IKC returns is an artifact of the order in which nodes are processed, combined with the constraint of disjoint clustering. If instead we allow ourselves to consider whether other nodes would be considered valid members of the clusters produced by IKC, we would ask very simply whether the addition of a given node to a particular cluster would maintain these properties; this is AOC\_k.  A more conservative expansion would say that we would not add a node to a cluster if it reduced the MCD score of the cluster (i.e., if it reduced the minimum degree within the cluster); this is AOC\_{m}.  In other words, the philosophy of AOC is imply to say that membership in a cluster should not be an accidental outcome of the algorithmic strategy for constructing the clusters; instead, it should reflect only the criterion for membership expressed by the cluster's minimum degree (if we wish to be conservative) or by the input to the IKC algorithm, which includes the parameter $k$.}. With respect to accuracy, the  use of marker nodes is to identify the subset of clusters of interest in this case and not to evaluate cluster quality. The question of irrelevant publications is unclear; these clusters are predicated on citation density, not keyword density or textual coherence for example, and they satisfy explicit criteria. Further, we indicate in the manuscript that the ultimate determination of value should be qualitative.

Thus, the expansion using AOC is not meant to ``improve accuracy" in the sense of being reflective of some true structure, but it is instead providing a fuller exploration of the ``meaning" of the clusters we obtained in the IKC portion of the IKC+AOC pipeline.  Having said this, we do feel that the AOC\_{m} version if closer to reflecting the true nature of a cluster. Thus, if a cluster expands under AOC\_{m}  to include many nodes, then we would argue that the expanded version  is a better representation of what that community means than the original version produced by IKC. 

\vspace{2 mm}  
\emph{It is not clear what to expect from the approach using the marker nodes. Are the marker nodes expected to be concentrated into one cluster for the clustering solution to be successful, or are the marker nodes delineated so that they represent different subareas? Preferably, this should have been made clear ex ante and the subareas explicated.}

\vspace{2 mm}  
As we mention above, the use of marker nodes is to identify the subset of clusters that are relevant. As we also explained in some detail in our first response, the network is constructed by a lexical search, which is expanded by harvesting citing and cited references to favor the chance of including semantically relevant publications. This inclusive strategy results in a large network, and the markers help identify those clusters of interest from among those generated by the method. The point about \emph{ex ante} specification is a very good one and we thank the reviewer for raising it. At this point, we are loath to start hypothesizing after results are known but we have added a paragraph in the Conclusions that addresses this point.

The marker node approach was useful in this case but high concentration of markers may not always occur for more than one reason. We have also considered labeling the markers according to subareas but finding agreement on appropriate labels is non-trivial. Thus, the only conclusion we draw from this study is that clusters 3, 4, and 25 are the ones to be studied to learn more about the exosome community. 

\vspace{2 mm}  
\emph{ I am surprised by the size of the clusters obtained, including a cluster with as much as 214,000 publications. The three clusters with most marker nodes (3,4 and 25) consist of almost 400,000 publications before AOC and 540,000 after AOC\_k. A search in PubMed on the MeSH-term “Extracellular Vesicles” renders about 23,000 publications (“Extracellular Vesicles”[mesh]). Dimensions have a wider coverage than PubMed but a search in titles and abstracts renders about the same number of publications. This is of course a rough estimate of the field. Nevertheless, it seems to me that the sizes of these clusters are unrealistic if they are supposed to correspond to subareas of the field of Extracellular Vesicles. Based on the large size of cluster 3 and 4 I suspect that the accuracy of these clusters is low. In addition, the sizes of these clusters do not correspond well with the previous literature on research communities, in particular research specialties (Boyack \& Klavans, 2014; Morris \& Van der Veer Martens, 2008; Scharnhorst et al., 2012; Sjogarde \& Ahlgren, 2020).}

\vspace{2 mm} 
The network contains k-cores of varying density and size and AOC augments them to overcome the limitations of disjoint clustering. The cluster sizes reflect iterative deterministic discovery of k-cores by IKC in the input network. If some clusters appear large, it is because those k-cores are large. We respectfully submit that clustering is an art as well as a science and lacks a ground truth (Luxburg, Williamson, and Guyon 2012) 
https://proceedings.mlr.press/v27/luxburg12a/luxburg12a.pdf). Practitioners tend to select parameters that will generate cluster sizes that serve their purpose. 

With respect to the PubMed search, the numbers quoted seem about right but the reviewer offers a limiting definition. Our definition is `lexical plus citation-linked', which is then reduced by clustering and selection of a subset of clusters. Thus, articles concerning electron microscopy, intracellular trafficking, endoplasmic reticulum, exocytosis, and endocytosis would quality. The following example may be useful. The founder papers of the field (Harding, Heuser, and Stahl, 1983 and Pan and Johnstone, 1983) do not mention exosome. It was coined by Rose Johnstone some years later see `Exosomes: Looking back three decades and into the future', 2013, https://doi.org/10.1083/jcb.201212113. The founder papers can be found by searching the references of other exosome papers but would not be found in a lexical search. They are in our network.


The studies cited by the reviewer are excellent and informative but incommensurable in direct comparison with our work. For example, Morris \& Van der veer Martens, 2008/9 refer largely to historical studies; Price in 1965 estimated  the research front being in the order of a `few hundred individuals'. We do not think this is likely in 2022. The remaining studies are more comparable. Waltman \& van Eck (2012) progressively agglomerate to a cognitively manageable number of clusters and discuss features of clusters at various stages of this process. Boyack and Klavans (2014) used co-citations and bibliographic coupling, which identify different patterns of relationships. Like us, Sjogarde \& Ahlgren (2020) also seek to identify publications associated with a specialty rather than the specialty's members. However, they use the definition of Morris and van der veer Martens (2008) in their thought process - that topics are shared within a speciality. We use citation density independent of topic. Sjogarde also uses Modularity Optimization and considers journals, which we do not.

We are not dismissing prior work though. In Wedell et al. (2022), we compare IKC clusters with those generated by the popular Leiden algorithm. We also describe cluster breaking strategies as user options in the same article but those are not the focus of this manuscript. However, we do mention it in the Introduction. `Subsequent steps in the pipeline include breaking large cores and adding peripheral nodes to each core to construct communities with core-periphery structure. While IKC is a necessary step in the pipeline, the remaining steps are optional.'

\vspace{2 mm} 
 \emph{The caption of Figure 6 gives information about the increased coverage of marker nodes in cluster 4, from 40.7\% to 94.6\% for AOC\_k. This must mean that around 550 marker nodes have been added to cluster 4 by the procedure. From table 2 we get to know that about 76,000 records have been added to reach this larger coverage. So less than 1\% of the nodes added to the cluster are marker nodes. These figures suggest that the accuracy of AOC is low.}
\vspace{2 mm} 

\vspace{2 mm} 
We have stated the purpose of marker nodes earlier-- for cluster identification and not for cluster quality evaluation or accuracy.

\vspace{2 mm} 
 \emph{ In my previous answer I had a comment about normalization. This comment seems to have been misinterpreted as field-normalization applied in evaluative bibliometrics. However, I am referring to normalization of edge weights in citation networks (E.g., see Ahlgren et al., 2003; Boyack et al., 2005; Waltman \& van Eck, 2012). Such normalization does not only normalize for differences between fields, but also for the highly skewed distribution of citations and temporality of citations. I agree that in some cases there are reasons to let highly cited publications have more influence on clustering (or the identification of cores) than publications with low citation counts. The reason I am mentioning normalization is to make the authors aware that the highly skewed distribution of cluster sizes and the problems I have raised above may be related to this issue. It seems to me that the full count approach leads to some very large clusters and low accuracy. This regards both the initial IKC and AOC. However, I do not impose any action from the authors regarding normalization.}
 
 \vspace{2 mm} 
 Thank you, this is relevant for our future work. We will comment that Waltman and van Eck normalized to correct for different citation behavior across fields. The normalizations used by Boyack et al. (2005) don't seem to be very relevant to our work and those measures are not being used by Boyack and Klavans today. Even so, the point is very well taken. 

\vspace{2 mm} 
 \emph{In summary, my main point is that the empirical part of the paper does not make it possible for the reader to judge to what degree AOC is successful in terms of coverage and accuracy. Therefore, I think the paper should be revised.}  
 
 \vspace{2 mm} 
 We have made revisions that consider the points raised by the reviewer and clarify those already made.

\vspace{2 mm} 
 \emph{Some minor comments:p. 16 “After AOC m treatment of IKC clusters, clusters 3, 4, and 25 contained 30.4\%, 42.5\%, and 93.1\%, respectively, of all markers.” This seem to be incorrect. It does not align with p. 18 “After AOC m treatment of IKC clusters, clusters 3, 4, and 25 contained 42.5\%, 90.2\%, and 30.4\% respectively, of all markers.” p. 16-17 “After AOC k treatment of IKC clusters, clusters 3, 4, and 25 contained 69.5\%, 71.8\%, and 94.6\% of all markers respectively.” Also this seem to be incorrect.} \\

We are confused by this. Perhaps the reviewer was looking across the multiple versions in the PDF generated by the journal- the original version, the corrections we described in our first response, and the first revision. 

\vspace{2 mm} 
The text in the first revision read: \emph{After AOC\_m treatment of IKC clusters, clusters 3, 4, and 25 contained 42.5\%, 90.2\%, and 30.4\% respectively, of all markers. After AOC\_k treatment of IKC clusters, clusters 3, 4, and 25 contained 60.5\%, 91.3\%, and 69.5\% of all markers respectively. Thus, clusters 3, 4, and 25 all expand more significantly under AOC k than under AOC m. We also note that cluster 1, which contains 2.4\% of markers in IKC and 4.8\% after AOC\_m, is significantly enriched for marker nodes by AOC\_k to 20.7\% of the marker nodes. These data suggest that the recursive approach of IKC results in markers being segregated by disjoint clustering, but this effect can be remediated by post-processing using AOC.}

\vspace{2 mm} 
In any case, the second revision contains the following text: \\

(1)  (page 17)   \emph{The count of cores with non-zero marker counts varied between treatments. For IKC, 17 of 128 cores exhibited non-zero marker counts. Clusters 3, 4, and 25 are notable in accounting for 87.5\% of 1021 markers after IKC clustering. Because of this substantial coverage of marker nodes, from the perspective of EV biology, clusters 3, 4, and 25 are of obvious interest and offer a significant reduction in the amount of information to be studied qualitatively.
After IKC+AOC treatment, 20 of 128 (AOC m) and 31 of 128 (AOC k) cores respectively contained non-zero marker counts, which is consistent with the relatively stringent and permissive designs of AOC\_m and AOC\_k respectively. After AOC\_m treatment of IKC clusters, clusters 3, 4, and 25 contained...}\\

(2) page 18 contains a figure\\

(3) (page 19 ) \emph{...42.5\%, 90.2\%, and 30.4\% respectively, of all markers. After AOC k treatment of IKC clusters, clusters 3, 4, and 25 contained 60.5\%, 91.3\%, and 69.5\% of all markers respectively. Thus, clusters 3, 4, and 25 all expand more significantly under AOC\_k than under AOC\_m. We also note that cluster 1, which contains 2.4\% of markers in IKC and 4.8\% after AOC\_m, is significantly enriched for marker nodes by AOC\_k to 20.7\% of the marker nodes. These data suggest that the recursive approach of IKC results in markers being segregated by disjoint clustering, but this effect can be remediated by post-processing using AOC.}


\vspace{4 mm}

Provided by the reviewer, for which we are thankful. 
\begin{itemize}
\item Requirements for a cocitation similarity measure, with special reference to Pearson’s correlation coefficient. (Ahlgren, 2003)
\item Creation of a highly detailed, dynamic, global model and map of science. Boyack and Klavans (2014)
\item Mapping the backbone of science. (Boyack et al. 2005) 
\item Mapping research specialties. (Morris and van der veer Martens 2008)
\item Models of Science Dynamics. Springer Berlin Heidelberg. (Scharnhorst et al. 2012)
\item Granularity of algorithmically constructed publication-level classifications of research publications: Identification of specialties. (Sjogarde and Ahlgren 2020)
\item A new methodology for constructing a publication-level classification system of science. (waltman and van Eck 2012)
\end{itemize}


\end{document}